\LaTeX\ Author Guidelines for ICCV Proceedings

### 2019-05-21 chapters/5_experiments_noise.tex
Updates from Overleaf

\begin{figure}[t]
        \centering
\begin{minipage}[t]{0.48\textwidth}
% \begin{table}
    \centering
    \scriptsize
    % \begin{subtable}[t!]{0.5\textwidth}\centering
        \begin{tabular}[t]{l|l|c}
        % \toprule
        % & \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\
         % & \multicolumn{1}{c}{\thead{\textsc{No}}} & \multicolumn{1}{c}{\thead{\textsc{Yes}}} \\ \midrule
         & \makecell[l]{\algname{}\\ Linkage} & \makecell{Cremi-Score \\(lower is better)} \\ \midrule 
         % & \multicolumn{1}{c}{\thead{$\beta$}}  & \thead{AP} & \multicolumn{1}{c}{\thead{$\beta$}} & \thead{AP} \\ \midrule\midrule
\textbf{\algname{}} & \textbf{Average}& \textbf{0.226}  \\
Greedy Fixation \cite{levinkov2017comparative} & Sum + Constr. & 0.282 \\
DTWS + MC & -& 0.310 \\
DTWS + LMC & -& 0.317 \\
Mutex Watershed \cite{wolf2018mutex} & Abs. Max.  & 0.322 \\
GAEC \cite{keuper2015efficient} & Sum & 0.334 \\
THRESH &-& 1.521 \\ 
% \textbf{\algname{}} & \textbf{Average}& \textbf{0.936 $\pm$ 0.004}  \\
% Greedy Fixation \cite{levinkov2017comparative} & Sum + Constr. & 0.906 $\pm$ 0.022 \\
% DTWS + LMC & -& 0.903 $\pm$ 0.016 \\
% DTWS + MC & -& 0.903 $\pm$ 0.017 \\
% % DTWS + avgHC &-& \\
% % DTWS + MC (SR)& -& 0.900 $\pm$ 0.019 \\
% % DTWS + LMC (SR)& -& 0.898 $\pm$ 0.017 \\
% Mutex Watershed \cite{wolf2018mutex} & Abs. Max.  & 0.897 $\pm$ 0.012 \\
% GAEC \cite{keuper2015efficient} & Sum & 0.872 $\pm$ 0.028 \\
% THRESH &-& 0.221  $\pm$ 0.067 \\ 
% % DTWS + \algname{} & Average& \TODO{} \\
% % DTWS  & -& 0.010 $\pm$ 0.003\\
        \end{tabular}
    \captionof{table}{Cremi-Scores achieved by different post-processing methods. Scores are averaged over the three CREMI training samples}
    \label{tab:results_cremi_train}
\end{minipage}\hfill
\begin{minipage}[t]{0.48\textwidth}
    \centering
    \scriptsize
        \begin{tabular}[t]{l|c}
         & \makecell{Cremi-Score \\(lower is better)}  \\ \midrule
\textbf{Our UNet + DTWS + LMC} &  \textbf{0.221}\\
PNI-UNet \UPDATE{[REF?]} & 0.228 \\
Our UNet + \algname{} Avg-Linkage & 0.241 \\
MALA-UNet + MC \cite{funke2018large} & 0.276 \\
CRUNet \cite{zeng2017deepem3d} & 0.566  \\
LFC \cite{parag2017anisotropic} & 0.616  \\
% Our UNet + DTWS + LMC &  \textbf{0.221} & \textbf{0.108}\\
% PNI-UNet & 0.228 & 0.116 \\
% Our UNet + \algname{} Avg-Linkage & 0.244 & 0.130 \\
% MALA-UNet + MC \cite{funke2018large} & 0.276 & 0.132 \\
% CRUNet \cite{zeng2017deepem3d} & 0.566 & 0.229 \\
% LFC \cite{parag2017anisotropic} & 0.616 & \\
        \end{tabular}
        \vspace*{1.1em}
    \captionof{table}{Current leaderboard of the CREMI challenge with the Cremi-Scores averaged over the three test samples}
    \label{tab:results_cremi_test}
\end{minipage}
\end{figure}
\captionsetup[subfigure]{justification=centering, singlelinecheck=off}
\begin{figure}
\centering
    %     \begin{subfigure}[t]{0.49 \textwidth}
    %     \centering
    %     \includegraphics[width=\textwidth,trim=0.55in 0.35in 0.65in 0.80in,clip]{./figs/merge_noise_only_direct.pdf}

>>>>

\begin{figure}[t]
        \centering
\begin{minipage}[t]{0.48\textwidth}
% \begin{table}
    \centering
    \scriptsize
    % \begin{subtable}[t!]{0.5\textwidth}\centering
        \begin{tabular}[t]{l|l|c}
        % \toprule
        % & \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\
         % & \multicolumn{1}{c}{\thead{\textsc{No}}} & \multicolumn{1}{c}{\thead{\textsc{Yes}}} \\ \midrule
         & \makecell[l]{\algname{}\\ Linkage} & \makecell{Cremi-Score \\(lower is better)} \\ \midrule 
         % & \multicolumn{1}{c}{\thead{$\beta$}}  & \thead{AP} & \multicolumn{1}{c}{\thead{$\beta$}} & \thead{AP} \\ \midrule\midrule
\textbf{\algname{}} & \textbf{Average}& \textbf{0.226}  \\
Greedy Fixation \cite{levinkov2017comparative} & Sum + Constr. & 0.282 \\
DTWS + MC & -& 0.310 \\
DTWS + LMC & -& 0.317 \\
Mutex Watershed \cite{wolf2018mutex} & Abs. Max.  & 0.322 \\
GAEC \cite{keuper2015efficient} & Sum & 0.334 \\
THRESH &-& 1.521 \\ 
% \textbf{\algname{}} & \textbf{Average}& \textbf{0.936 $\pm$ 0.004}  \\
% Greedy Fixation \cite{levinkov2017comparative} & Sum + Constr. & 0.906 $\pm$ 0.022 \\
% DTWS + LMC & -& 0.903 $\pm$ 0.016 \\
% DTWS + MC & -& 0.903 $\pm$ 0.017 \\
% % DTWS + avgHC &-& \\
% % DTWS + MC (SR)& -& 0.900 $\pm$ 0.019 \\
% % DTWS + LMC (SR)& -& 0.898 $\pm$ 0.017 \\
% Mutex Watershed \cite{wolf2018mutex} & Abs. Max.  & 0.897 $\pm$ 0.012 \\
% GAEC \cite{keuper2015efficient} & Sum & 0.872 $\pm$ 0.028 \\
% THRESH &-& 0.221  $\pm$ 0.067 \\ 
% % DTWS + \algname{} & Average& \TODO{} \\
% % DTWS  & -& 0.010 $\pm$ 0.003\\
        \end{tabular}
    \captionof{table}{Cremi-Scores achieved by different post-processing methods. Scores are averaged over the three CREMI training samples}
    \label{tab:results_cremi_train}
\end{minipage}\hfill
\begin{minipage}[t]{0.48\textwidth}
    \centering
    \scriptsize
        \begin{tabular}[t]{l|c}
         & \makecell{Cremi-Score \\(lower is better)}  \\ \midrule
\textbf{Our UNet + DTWS + LMC} &  \textbf{0.221}\\
PNI-UNet \cite{lee2017superhuman} & 0.228 \\
Our UNet + \algname{} Avg-Linkage & 0.241 \\
MALA-UNet + MC \cite{funke2018large} & 0.276 \\
CRUNet \cite{zeng2017deepem3d} & 0.566  \\
LFC \cite{parag2017anisotropic} & 0.616  \\
% Our UNet + DTWS + LMC &  \textbf{0.221} & \textbf{0.108}\\
% PNI-UNet & 0.228 & 0.116 \\
% Our UNet + \algname{} Avg-Linkage & 0.244 & 0.130 \\
% MALA-UNet + MC \cite{funke2018large} & 0.276 & 0.132 \\
% CRUNet \cite{zeng2017deepem3d} & 0.566 & 0.229 \\
% LFC \cite{parag2017anisotropic} & 0.616 & \\
        \end{tabular}
        \vspace*{1.1em}
    \captionof{table}{Current leaderboard of the CREMI challenge with the Cremi-Scores averaged over the three test samples}
    \label{tab:results_cremi_test}
\end{minipage}
\end{figure}
\captionsetup[subfigure]{justification=centering, singlelinecheck=off}
\begin{figure}
\centering
    %     \begin{subfigure}[t]{0.49 \textwidth}
    %     \centering
    %     \includegraphics[width=\textwidth,trim=0.55in 0.35in 0.65in 0.80in,clip]{./figs/merge_noise_only_direct.pdf}
